---
title       : Shiny App Pitch
subtitle    : A brief presentation
author      : Pablo López-García
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 1: Aim of the presentation

1. Introduce the Shiny App developed in the course
2. Explaining how to run it

--- .class #id 

## Slide 2: Shiny App

1. Aim: to show the differences between the normal an exponential distribution
2. How? By plotting histograms of both distributions
3. The shiny app is available online here: https://plopezgarcia.shinyapps.io/shiny-app/

---
## Slide 3: Normal distribution histogram

```{r, echo=FALSE}
library(ggplot2)
qplot(rnorm(100, 0, 1))
```

---
## Slide 4: Exponential distribution histogram

```{r, echo=FALSE}
qplot(rexp(100))
```

---
## Slide 5: Conclusion

We have presented the differences between the normal and explonential distribution graphically.
